%%%%%%
% sajinmp - resume
% Uses LaTeX and moderncv
%%%%%%

\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{classic}

\usepackage[utf8]{inputenc} % character encoding
\usepackage[scale=0.85]{geometry} % adjust the page margins
\setlength{\separatorcolumnwidth}{0.6cm}


\AtBeginDocument{\setlength{\maketitlenamewidth}{10cm}}
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Sajin}
\familyname{M Prasad}
\title{Resume}
\mobile{+971-565232714}
\email{sajinprasadkm@gmail.com}
\homepage{sajinmp.com}
\extrainfo{Github: \href{https://github.com/sajinmp}{sajinmp}}

% --------------------------------------
% CONTENT
% --------------------------------------


\begin{document}
\maketitle

% --------------------------------------
% SUMMARY
% --------------------------------------

\section{Summary}
\begin{itemize}
    \setlength\itemsep{5pt}
    \item 10+ years of total experience in architecting, developing, testing and scaling of web applications.
    \item 9+ years of experience in application development with ruby.
    \item 7 years of experience in development and design of micro-services systems in ruby on rails.
    \item 8 years of experience in AWS (Amazon Web Services) which includes EC2, ELB, ECS, ECS Fargate, IAM, CloudWatch, SNS, SES, MediaConvert, Api Gateway, CloudFront, Lambda, Lambda@edge, ElasticCache, ElasticSearch, RDS, Aurora, Route53.
    \item 7 years of experience in Docker.
    \item Experienced in MySql, PostgresQL, MongoDB and SQLite
    \item Experienced in moving a monolithic application into microservices.
    \item Experience with database migrations.
    \item Extensive experience in linux and bash.
    \item Implemented CI/CD and implemented TDD in multiple applications.
    \item Built multiple applications from scratch to market and scale.
    \item Experienced in leading teams and mentoring.
    
\end{itemize}

\vspace{10pt}
\section{Technical skills}
\cvcomputer
{\textbf{Languages}}{Ruby, Bash, JavaScript, Python, HTML/CSS/Haml/SaSS, Liquid}
{\textbf{Frameworks}}{Ruby on Rails, jQuery, Jekyll, Bootstrap, Express.js}
\vspace{10pt}
\cvcomputer
{\textbf{Databases}}{PostgreSQL, MySQL, MongoDB, SQLite}
{\textbf{Cloud Providers}}{AWS, GCP, Heroku, DigitalOcean}
\vspace{10pt}
\cvcomputer
{\textbf{DevOps}}{Docker, Github Actions, TravisCI \\ CircleCI, AWS Cloudformation}
{\textbf{Other Tools}}{ElasticSearch, Jira/Confluence, \LaTeX}


% --------------------------------------
% WORK EX
% --------------------------------------


\vspace{10pt}
\section{Work Experience and Positions}

\cventry{May 2021 -- July 2024}{Lead Backend Engineer}{The Mobility Methods LLC}{Remote/California}{https://jen.health}{Lead of the team. Designed and built the flagship product Jen Health while taking care of its DevOps and scalability.\\%
\vspace{-1mm}
   \begin{itemize}
       \item[-] Collaborating and working with business stake holders, service providers and the development team.
       \item[-] Architecture decisions for the entire platform.
       \item[-] Single handedly managed the development of the backend of the product.
       \item[-] Designed and managed the infrastructure for the entire platform.
       \item[-] Monitoring and ensuring security and performance of the platform.
       \item[-] Building internal software systems.
   \end{itemize}
}

\vspace{10pt}

\cventry{May 2019 -- Apr 2021}{Senior Engineer}{Commutatus}{Remote/Chennai}{https://commutatus.com}{Designed and implemented solutions for various clients of Commutatus. Notable work - \\%
    \begin{itemize}\setlength\itemindent{10pt}
       \item {\textbf{AIESEC} -- {\small \href{https://aiesec.org}{https://aiesec.org}}
       \vspace{5pt}%
           \begin{itemize}\setlength\itemindent{10pt}
               \item[-] Switched application to serverless AWS Fargate and database to AWS Aurora.
               \item[-] Added test coverage and improved CI/CD pipeline.
               \item[-] Migrated the application to jruby and grape APIs to graphql.
               \item[-] Upgraded elasticsearch and docker. Upgraded graphql to class based API.
               \item[-] Increased the application performance by 15\% and reduced database size by 20\%.
               \item[-] Implemented alerting systems and improved the monitoring setup.
           \end{itemize}
       }
    \end{itemize}
}
\vspace{10pt}
\cventry{Aug 2017 -- Mar 2019}{Senior Engineer}{TongueStun Food Network Pvt. Ltd. (Acquired by Zomato)}{Bangalore}{https://tonguestun.com}{Designed and implemented solutions for flagship product e2z (now Food@Work). Developed and built other supporting services which form the e2z ecosystem.\\%
    \begin{itemize}\setlength\itemindent{10pt}
       \item {\textbf{E2z (now Food@work)} -- {\small \href{https://play.google.com/store/apps/details?id=com.tonguestun.order}{https://play.google.com/apps?id=com.tonguestun.order}}
       \vspace{5pt}%
           \begin{itemize}\setlength\itemindent{10pt}
               \item[-] Migrated from monolith to micro-services.
               \item[-] Brainstormed and built offline ordering to handle slow/no network connectivity.
               \item[-] Setup a service for on-demand and automated report generation.
               \item[-] Built a fraud detection system.
               \item[-] Implemented a complete tech support solution for the customer support team.
               \item[-] Contributed to the automated vendor payout solution (Finance dashboard/service).
           \end{itemize}
       }
    \end{itemize}
}
\vspace{10pt}
\cventry{Nov 2016 -- Jul 2017}{Tech Lead}{foOfys Solutions}{Bangalore}{https://foofys.com}{Headed the tech team. Designed and built solutions and managed projects for various clients of foOfys.}
\vspace{10pt}
\cventry{Mar 2016 -- Oct 2016}{Senior Developer}{foOfys Solutions}{Bangalore}{https://foofys.com}{Designed and built solutions for projects from various clients of foOfys.}
\vspace{10pt}
\cventry{Jul 2015 -- Jan 2016}{Software Developer}{Chergo E-Commerce Pvt. Ltd.}{Bangalore}{https://coursemantra.com}{Designed and implemented solutions for the flagship product CourseMantra.}
\vspace{10pt}
\cventry{Mar 2012 -- Dec 2012}{Application Tester}{Bang The Table}{Remote/Part-time}{https://bangthetable.com}{Worked with the QA team and made sure that the applications developed by Bang The Table work properly in as many browser/operating system permutations as possible.}


% --------------------------------------
% Education
% --------------------------------------


\vspace{10pt}
\section{Education}

\cvlistitem{\textbf{Bachelor's degree in Computer Science and Engineering}}


% --------------------------------------
% PROJECTS
% --------------------------------------


%\pagebreak
\vspace{10pt}
\section{Open Source Contributions}

\cvlistitem
{\textbf{Spotlight Search} -- {\small \href{https://github.com/commutatus/spotlight-search}{https://github.com/commutatus/spotlight-search}}
  \\Ruby gem that helps in filtering, sorting and exporting tables easier.
}


% --------------------------------------
% Hobby projects
% --------------------------------------


\vspace{10pt}
\section{Pet/Freelance Projects}

\cvlistitem
{\textbf{HolyMatha Academy App} -- {\small \href{https://play.google.com/store/apps/details?id=com.holymathamobileapp}{https://play.google.com/apps?id=com.holymathamobileapp}} (Terminated)
  \\Built an app for students of an academy to play the video recordings during the time of Covid-19.
}

\vspace{5pt}

\cvlistitem
{\textbf{Nerdzz} -- {\small \href{https://nerdzz.in}{https://nerdzz.in}} (Terminated)
  \\Founded Nerdzz to help students in campus learn the skills which would make them job ready, thereby solving the problem of finding new talent for the firm during the time.
}

\vspace{5pt}

\cvlistitem
{\textbf{GoodDay - Spread a smile campaign} -- {\small \href{https://britannia.herokuapp.com}{https://britannia.herokuapp.com}} (Terminated)
  \\One-page website that posts to twitter, built during the spread a smile campaign by Britannia.
}

% \vspace{5pt}

% \cvlistitem
% {\textbf{Endrrat} -- {\small \href{https://endrrat.ae}{https://endrrat.ae}}
%   \\One-page website for a toner company.
% }


% --------------------------------------
% Achievements ETC.
% --------------------------------------


\vspace{10pt}
\section{Achievements}

\cventry{Feb 2014}{C Coding}{Naipunya Institute of Management and Information
Technology}{Thrissur}{}
{Won second prize in national level C coding competition conducted as a part of Laqshya tech fest.}

\cventry{Feb 2012}{Shell Scripting Contest - Scriptaculous}{TKM College of Engineering}{Kollam}{}
{Won first prize in national level Shell scripting competition conducted as a part of Conjura tech fest.}


% --------------------------------------
% TALKS ETC.
% --------------------------------------


\vspace{10pt}
\section{Talks and Workshops}

\cventry{Jun 2019}{Why side projects fail?}{Commutatus}{Chennai}{}
{Gave a talk on why side projects fail.}

\cventry{May 2016}{Why side projects fail?}{foOfys Solutions}{Bangalore}{}
{Gave a talk on why side projects fail.}

\cventry{Aug 2014}{Git Version Control System}{Palakkad Institue of Science and Technology}{Palakkad}{}
{Led an introductory workshop on Git version control system for final year students.}


%------------------------------------------


\end{document}
