%%%%%%
% sajinmp - resume
% Uses LaTeX and moderncv
%%%%%%

\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{classic}

\usepackage[utf8]{inputenc} % character encoding
\usepackage[scale=0.8]{geometry} % adjust the page margins

\AtBeginDocument{\setlength{\maketitlenamewidth}{10cm}}
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Sajin}
\familyname{M Prasad}
\title{Resume}
\address{Karthika, Koratty South P O\\Thrissur, Kerala, India}{ - 680308}
\mobile{+91-9745165109}
\email{sajinprasadkm@gmail.com}
\homepage{sajinmp.com}
\extrainfo{Github: \href{https://github.com/sajinmp}{sajinmp}}

% --------------------------------------
% CONTENT
% --------------------------------------

\begin{document}
\maketitle

\section{Technical skills}
\cvcomputer
{\textbf{Languages}}{Ruby, Python, JavaScript, HTML/CSS/Haml/SaSS, Liquid, Bash}
{\textbf{Frameworks}}{Ruby on Rails, Jekyll, jQuery\\Bootstrap}
\cvcomputer
{\textbf{DevOps}}{AWS, Heroku, Digital Ocean, Docker}
{\textbf{Software Packages}}{PostgreSQL, MySQL, \LaTeX\\MongoDB, ElasticSearch}

% --------------------------------------
% WORK EX
% --------------------------------------

\section{Work Experience and Positions}

\cventry{May 2021 -- Present}{Back-end \& Site Reliability Engineer}{The Mobility Methods LLC}{https://jen.health}{}{Lead of the team. Designed and built the flagship product Jen Health while taking care of its DevOps and scalability.\\%
    \begin{itemize}\setlength\itemindent{10pt}
       \item {\textbf{Jen.Health} -- {\small \href{https://jen.health}{https://jen.health}}
       \vspace{5pt}
       \newline
       {Jen health helps you improve your mobility, reduce pain and build strength with knowledge \& exercises from experienced doctors of physical therapy.}%
       \vspace{5pt}
           \begin{itemize}\setlength\itemindent{10pt}
               \item[-] Designed and implemented the entire back-end and internal management platform
               \item[-] Setup the video conversion and streaming infrastructure
               \item[-] Built solution for tracking video playback and history
               \item[-] Setup postgresql full text search to rank and categorize videos
           \end{itemize}
       }
    \end{itemize}
}
\vspace{10pt}
\cventry{May 2019 -- Apr 2021}{Senior Engineer}{Commutatus}{https://commutatus.com}{}{Designed and implemented solutions for projects from various clients of Commutatus along with handling the infrastructure.\\%
    \begin{itemize}\setlength\itemindent{10pt}
       \item {\textbf{AIESEC} -- {\small \href{https://aiesec.org}{https://aiesec.org}}
       \vspace{5pt}
       \newline
       {AIESEC is an international youth-run, non-governmental and not-for-profit organization that provides young people with leadership development, cross-cultural internships, and global volunteer exchange experiences.}%
       \vspace{5pt}
           \begin{itemize}\setlength\itemindent{10pt}
               \item[-] Moved the application to AWS Fargate and database from AWS RDS to AWS Aurora
               \item[-] Added tests. Improved CI/CD to run tests and notify monitoring system of deployment
               \item[-] Migrated the application to jruby. Upgraded graphql, elasticsearch and docker
               \item[-] Tuned the application performance and reduced database size by 10\%
           \end{itemize}
       }
       \vspace{10pt}
       \item {\textbf{MentorMind} -- {\small \href{https://mentormind.in}{https://mentormind.in}}
       \vspace{5pt}
       \newline
       {MentorMind offers virtual, mentored work experiences that are co-created with top companies to help you build real skills in careers of your choice.}%
       \vspace{5pt}
           \begin{itemize}\setlength\itemindent{10pt}
               \item[-] Improved the application performance and code structure
               \item[-] Improved CI/CD pipeline to notify monitoring system of deployment
           \end{itemize}
       }
    \end{itemize}
}
\vspace{10pt}
\cventry{Aug 2017 -- Mar 2019}{Senior Engineer}{TongueStun Food Network Pvt. Ltd (Acquired by Zomato)}{https://tonguestun.com}{}{Designed and implemented solutions for flagship product e2z (now Food@Work). Developed and built other supporting applications which form the e2z ecosystem.\\%
    \begin{itemize}\setlength\itemindent{10pt}
       \item {\textbf{E2z (now Food@work)} -- {\small \href{https://play.google.com/store/apps/details?id=com.tonguestun.order}{https://play.google.com/apps?id=com.tonguestun.order}}
       \vspace{5pt}
       \newline
       {E2z is the flagship product of Tonguestun aiming at digitizing cafeterias by connecting food vendors to companies. This app is for the employees of the company to order food from the vendors in their company cafeteria. The e2z ecosystem consists of various applications which caters to providing a great cafeteria experience.}%
       \vspace{5pt}
           \begin{itemize}\setlength\itemindent{10pt}
               \item[-] Moved from monolith to micro-services
               \item[-] Experimented and built an option to order offline via app for when internet is slow
               \item[-] Came up with a fraud detection system
               \item[-] Setup a service for generating various types of reports based on transaction data
               \item[-] Brainstormed and came up with an idea for a finance dashboard to track and process vendor payments easier and automated
           \end{itemize}
       }
    \end{itemize}
}
\vspace{10pt}
\cventry{Nov 2016 -- Jul 2017}{Tech Lead}{foOfys Solutions}{https://foofys.com}{}{Headed the tech team. Designed and built solutions and managed projects for various clients of foOfys.}
\vspace{10pt}
\cventry{Mar 2016 -- Oct 2016}{Senior Developer}{foOfys Solutions}{https://foofys.com}{}{Designed and built solutions for projects from various clients of foOfys.}
\vspace{10pt}
\cventry{Jul 2015 -- Jan 2016}{Software Developer}{Chergo E-Commerce Pvt. Ltd.}{https://coursemantra.com}{}{Designed and implemented solutions for the flagship product CourseMantra while taking care of its DevOps, scalability and security.}
\vspace{10pt}
\cventry{Mar 2012 -- Dec 2012}{Application Tester}{Bang The Table}{https://bangthetable.com}{}{Worked with the QA team and made sure that the applications developed by Bang The Table work properly in as many browser/operating system permutations as possible.}



% --------------------------------------
% PROJECTS
% --------------------------------------

%\pagebreak
\section{Open Source Contributions}

\cvlistitem
{\textbf{Spotlight Search} -- {\small \href{https://github.com/commutatus/spotlight-search}{https://github.com/commutatus/spotlight-search}}
  \\Ruby gem that helps in filtering, sorting and exporting tables easier.
}

\vspace{5pt}

\cvlistitem
{\textbf{Vimeo Upload} -- {\small \href{https://rubygems.org/gems/vimeo\_upload}{https://rubygems.org/gems/vimeo\_upload}}
  \\Ruby gem for uploading video to vimeo.
}

% --------------------------------------
% Hobby projects
% --------------------------------------

\section{Pet Projects}

\cvlistitem
{\textbf{Holy Matha Academy App} -- {\small \href{https://play.google.com/store/apps/details?id=com.holymathamobileapp}{https://play.google.com/apps?id=com.holymathamobileapp}} (Terminated)
  \\Built an app for students of a friend's academy to play the video recordings during the time of Covid-19.
}

\vspace{5pt}

\cvlistitem
{\textbf{Nerdzz} -- {\small \href{https://nerdzz.in}{https://nerdzz.in}} (Terminated)
  \\Founded Nerdzz to help students in campus learn the skills which would make them job ready, thereby solving the problem of finding new talent for the firm during the time.
}

\vspace{5pt}

\cvlistitem
{\textbf{GoodDay - Spread a smile campaign} -- {\small \href{https://britannia.herokuapp.com}{https://britannia.herokuapp.com}}
  \\One-page website that posts to twitter, built during the spread a smile campaign by Britannia.
}

\break

% --------------------------------------
% TALKS ETC.
% --------------------------------------

\section{Talks and Workshops}
\cventry{Jun 2019}{Why side projects fail?}{Commutatus}{}{Credit: \href{https://blog.revathskumar.com/p/about-me.html}{Revath S Kumar}}
{Gave a talk on why side projects fail.}
\cventry{May 2016}{Why side projects fail?}{foOfys Solutions}{}{}
{Gave a talk on why side projects fail.}
\cventry{Aug 2014}{Git Version Control System}{Palakkad Institue of Science and Technology}{}{}
{Led an introductory workshop on Git version control system for final year students.}


% --------------------------------------
% Achievements ETC.
% --------------------------------------

\section{Achievements}
\cventry{Feb 2014}{C Coding}{Naipunya Institute of Management and Information
Technology}{Thrissur}{}
{Won second prize in national level C coding competition conducted as a part of Laqshya tech fest.}
\cventry{Feb 2012}{Shell Scripting Contest - Scriptaculous}{TKM College of Engineering}{Kollam}{}
{Won first prize in national level Shell scripting competition conducted as a part of Conjura tech fest.}

%------------------------------------------


\end{document}
