%%%%%%
% sajinmp - resume
% Uses LaTeX and moderncv
%%%%%%

\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{classic}

\usepackage[utf8]{inputenc} % character encoding
\usepackage[scale=0.85]{geometry} % adjust the page margins
\setlength{\separatorcolumnwidth}{0.6cm}


\AtBeginDocument{\setlength{\maketitlenamewidth}{10cm}}
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Sajin}
\familyname{M Prasad}
\title{Resume}
\mobile{+971-565232714}
\email{sajinprasadkm@gmail.com}
\homepage{sajinmp.com}
\extrainfo{Github: \href{https://github.com/sajinmp}{sajinmp}}

% --------------------------------------
% CONTENT
% --------------------------------------


\begin{document}
\maketitle

% --------------------------------------
% SUMMARY
% --------------------------------------

\section{Summary}

Software engineer with more than 10 years of experience building software to solve real-life problems. Started as a full stack developer and 5 years later moved to focus on back-end and infrastructure. Has executed numerous web/mobile development projects in all stages of the software development life cycle (with Ruby on Rails and related technologies). Has the ability to plan, execute and build large and complex projects working with the business stakeholders.

\vspace{10pt}
\begin{itemize}
    \setlength\itemsep{5pt}
    \item Built multiple applications from scratch to market to scale.
    \item Enjoys building stuff and works at a high pace without compromising quality.
    \item Loves solving problems and enjoys a creative solution even more.
    \item Quick in solving bugs/issues.
    \item Enjoys learning new things.
    \item Good communication skills.
    
\end{itemize}

\vspace{10pt}
\section{Technical skills}
\cvcomputer
{\textbf{Languages}}{Ruby, Bash, JavaScript, Python, HTML/CSS/Haml/SaSS, Liquid}
{\textbf{Frameworks}}{Ruby on Rails, jQuery, Jekyll, Bootstrap, Express.js}
\vspace{10pt}
\cvcomputer
{\textbf{Databases}}{PostgreSQL, MySQL, MongoDB, SQLite}
{\textbf{Cloud Providers}}{AWS, GCP, Heroku, DigitalOcean}
\vspace{10pt}
\cvcomputer
{\textbf{DevOps}}{Docker, Github Actions, TravisCI \\ CircleCI, AWS Cloudformation}
{\textbf{Other Tools}}{ElasticSearch, Jira/Confluence, \LaTeX}

% --------------------------------------
% WORK EX
% --------------------------------------


\vspace{10pt}
\section{Work Experience and Positions}

\cventry{May 2021 -- July 2024}{Lead Backend Engineer}{The Mobility Methods LLC}{Remote/California}{https://jen.health}{Lead of the team. Designed and built the flagship product Jen Health while taking care of its DevOps and scalability.\\%
\vspace{-1mm}
   \begin{itemize}
       \item[-] Collaborating and working with business stake holders, service providers and the development team.
       \item[-] Architecture decisions for the entire platform.
       \item[-] Single handedly managed the development of the backend of the product.
       \item[-] Planned and handled feature development and handled production bugs/issues raised by customers
       \item[-] Designed and managed the infrastructure for the entire platform.
       \item[-] Works with all the third party partners for integration and smooth running of their services with Jen.Health ecosystem.
       \item[-] Monitoring and ensuring security and performance of the platform.
       \item[-] Building internal software systems.
   \end{itemize}
}

\vspace{10pt}

\cventry{May 2019 -- Apr 2021}{Senior Engineer}{Commutatus}{Remote/Chennai}{https://commutatus.com}{Designed and implemented solutions for various clients of Commutatus. Notable work - \\%
    \begin{itemize}\setlength\itemindent{10pt}
       \item {\textbf{AIESEC} -- {\small \href{https://aiesec.org}{https://aiesec.org}}
       \vspace{5pt}%
           \begin{itemize}\setlength\itemindent{10pt}
               \item[-] Switched application to AWS ECS on Fargate and database to AWS Aurora.
               \item[-] Added test coverage and improved CI/CD pipeline.
               \item[-] Migrated the application to jruby and grape based REST APIs to graphql.
               \item[-] Upgraded elasticsearch and docker. Upgraded graphql to class based API.
               \item[-] Increased the application performance by 15\% and reduced database size by 20\%.
               \item[-] Implemented alerting systems and improved the monitoring setup.
           \end{itemize}
       }
    \end{itemize}
}
\vspace{10pt}
\cventry{Aug 2017 -- Mar 2019}{Senior Engineer}{TongueStun Food Network Pvt. Ltd. (Acquired by Zomato)}{Bangalore}{https://tonguestun.com}{Designed and implemented solutions for flagship product e2z (now Food@Work). Developed and built other supporting services which form the e2z ecosystem.\\%
    \begin{itemize}\setlength\itemindent{10pt}
       \item {\textbf{E2z (now Food@work)} -- {\small \href{https://play.google.com/store/apps/details?id=com.tonguestun.order}{https://play.google.com/apps?id=com.tonguestun.order}}
       \vspace{5pt}%
           \begin{itemize}\setlength\itemindent{10pt}
               \item[-] Migrated from monolith to micro-services.
               \item[-] Planned, designed and built offline ordering to handle slow/no network connectivity.
               \item[-] Setup service for on-demand and automated report generation.
               \item[-] Built a fraud detection system based on user data and behavior.
               \item[-] Implemented a complete tech support solution for the customer support team.
               \item[-] Contributed to the automated vendor payout solution (Finance dashboard/service).
           \end{itemize}
       }
    \end{itemize}
}
\vspace{10pt}
\cventry{Nov 2016 -- Jul 2017}{Tech Lead}{foOfys Solutions}{Bangalore}{https://foofys.com}{Headed the tech team. Designed and built solutions and managed projects for various clients of foOfys.}
\vspace{10pt}
\cventry{Mar 2016 -- Oct 2016}{Senior Developer}{foOfys Solutions}{Bangalore}{https://foofys.com}{Designed and built solutions for projects from various clients of foOfys.}
\vspace{10pt}
\cventry{Jul 2015 -- Jan 2016}{Software Developer}{Chergo E-Commerce Pvt. Ltd.}{Bangalore}{https://coursemantra.com}{Designed and implemented solutions for the flagship product CourseMantra.}
\vspace{10pt}
\cventry{Mar 2012 -- Dec 2012}{Application Tester}{Bang The Table}{Remote/Part-time}{https://bangthetable.com}{Worked with the QA team and made sure that the applications developed by Bang The Table work properly in as many browser/operating system permutations as possible.}


% --------------------------------------
% Education
% --------------------------------------


\vspace{10pt}
\section{Education}

\cvlistitem{\textbf{Bachelor's degree in Computer Science and Engineering}}


% --------------------------------------
% PROJECTS
% --------------------------------------


%\pagebreak
\vspace{10pt}
\section{Open Source Contributions}

\cvlistitem
{\textbf{Spotlight Search} -- {\small \href{https://github.com/commutatus/spotlight-search}{https://github.com/commutatus/spotlight-search}}
  \\Ruby gem that helps in filtering, sorting and exporting tables easier.
}


% --------------------------------------
% Hobby projects
% --------------------------------------


\vspace{10pt}
\section{Pet/Freelance Projects}

\cvlistitem
{\textbf{HolyMatha Academy App} -- {\small \href{https://play.google.com/store/apps/details?id=com.holymathamobileapp}{https://play.google.com/apps?id=com.holymathamobileapp}} (Terminated)
  \\Built an app for students of an academy to play the video recordings during the time of Covid-19.
}

\vspace{5pt}

\cvlistitem
{\textbf{Nerdzz} -- {\small \href{https://nerdzz.in}{https://nerdzz.in}} (Terminated)
  \\Founded Nerdzz to help students in campus learn the skills which would make them job ready, thereby solving the problem of finding new talent for the firm during the time.
}

\vspace{5pt}

\cvlistitem
{\textbf{GoodDay - Spread a smile campaign} -- {\small \href{https://britannia.herokuapp.com}{https://britannia.herokuapp.com}} (Terminated)
  \\One-page website that posts to twitter, built during the spread a smile campaign by Britannia.
}

% \vspace{5pt}

% \cvlistitem
% {\textbf{Endrrat} -- {\small \href{https://endrrat.ae}{https://endrrat.ae}}
%   \\One-page website for a toner company.
% }


% --------------------------------------
% Achievements ETC.
% --------------------------------------


\vspace{10pt}
\section{Achievements}

\cventry{Feb 2014}{C Coding}{Naipunya Institute of Management and Information
Technology}{Thrissur}{}
{Won second prize in national level C coding competition conducted as a part of Laqshya tech fest.}

\cventry{Feb 2012}{Shell Scripting Contest - Scriptaculous}{TKM College of Engineering}{Kollam}{}
{Won first prize in national level Shell scripting competition conducted as a part of Conjura tech fest.}


% --------------------------------------
% TALKS ETC.
% --------------------------------------


\vspace{10pt}
\section{Talks and Workshops}

\cventry{Jun 2019}{Why side projects fail?}{Commutatus}{Chennai}{}
{Gave a talk on why side projects fail.}

\cventry{May 2016}{Why side projects fail?}{foOfys Solutions}{Bangalore}{}
{Gave a talk on why side projects fail.}

\cventry{Aug 2014}{Git Version Control System}{Palakkad Institue of Science and Technology}{Palakkad}{}
{Led an introductory workshop on Git version control system for final year students.}


%------------------------------------------


\end{document}
